Use of the package \texttt{fitdistrplus} to specify a distribution from non-censored or censored data

### 2011-03-14 inst/doc/intro2fitdistrplus.Rnw
minor corrections on .Rd files and vignette

\subsection{Maximum goodness-of-fit estimation}
%%%%%%%%%%
Parameters may also be estimated by maximizing a goodness-of-fit distance
by fixing the argument \texttt{method}
to \texttt{"mge"} in the call to fitdist and adding an argument \texttt{gof}
coding for the goodness-of-fit distance chosen. One may use the classical 
Cramer-von Mises distance (\texttt{"CvM"}), the classical
Kolmogorov-Smirnov distance (\texttt{"KS"}), the classical Anderson-Darling distance (\texttt{"AD"})
which gives more weight to the tails of the distribution,
or one of the variants of this last distance (see the help file page of the function
\texttt{mgedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by maximizing the 
Kolmogorov-Smirnov distance.
<<>>=
fitdist(u,"unif",method="mge",gof="KS")
@

>>>>

\subsection{Maximum goodness-of-fit estimation}
%%%%%%%%%%
Parameters may also be estimated by maximizing goodness-of-fit (or minimizing a goodness-of-fit distance)
by fixing the argument \texttt{method}
to \texttt{"mge"} in the call to fitdist and adding an argument \texttt{gof}
coding for the goodness-of-fit distance chosen. One may use the classical 
Cramer-von Mises distance (\texttt{"CvM"}), the classical
Kolmogorov-Smirnov distance (\texttt{"KS"}), the classical Anderson-Darling distance (\texttt{"AD"})
which gives more weight to the tails of the distribution,
or one of the variants of this last distance (see the help file page of the function
\texttt{mgedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by maximizing the 
Kolmogorov-Smirnov distance.
<<>>=
fitdist(u,"unif",method="mge",gof="KS")
@
